My First R Marckdown Doc
========================

My First markdwon file

I used I used the info [here](https://rpubs.com/sureshbk/358994) and [here](https://rstudio-pubs-static.s3.amazonaws.com/300758_367ce30144b44cd4901bedfa279bb64c.html) to complete the assignment.

# I downloaded the data set, and I set my directory 
```{r}
setwd ("C:/Users/Charlotte/Documents/GitHub/RepData_PeerAssessment1")
```

# Open/load the file
```{r}
DataFrame <- read.csv( "activity.csv")
```

spent an hr with errors trying to figure out how install packages in Kniter until I figure out on the net U don't. Why wouldn't the lectures cover that ... Wow? I used 
1. install.packages("dplyr")
2. install.packages("ggplot2") 
3. install.packages("magrittr")
4. library(tidyverse)

# Calculate the total number of steps taken per day?
Get number of steps per date and sum results removing null
```{r}
totalstepsperday <- aggregate(steps ~ date, data = DataFrame, FUN = sum, na.rm = TRUE)
```
put date in YYYYMMDD format
```{r}
DataFrame$date <- as.Date(DataFrame$date, "%Y-%m-%d")
```
Make a histogram of the total number of steps taken each day. convert dates first
A "Histograms are used to show distributions of variables while bar charts are used to compare variables.
Via [Forbes mag](https://www.forbes.com/sites/naomirobbins/2012/01/04/a-histogram-is-not-a-bar-chart/?sh=27f69e816d77)
```{r}
hist(totalstepsperday$steps, main = "steps per Day", breaks = 10)
```


# Calculate and report the mean and median total number of steps taken per day.
calculate the mean:
```{r}
mean_steps <- mean(totalstepsperday$steps)
mean_steps
```
#Calculate median
```{r}
median_steps <- median(totalstepsperday$steps)
median_steps
```

# NEXT What is the average daily activity pattern?
Make a time series plot (of type 1) the 5-minute interval (x-axis)and the average number of steps taken, averaged across all days (y-axis).

#Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
#From the DataFrame create dataset making Steps a dependent variable of interval 
```{r}
fivemin <- aggregate(steps ~ interval, data = DataFrame, FUN = mean, na.rm = TRUE)
plot (x = fivemin$interval, y = fivemin$steps, type = "l", main = "5-minute interval")
```


# Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
five_min_maxsteps <- fivemin$interval[which.max(fivemin$steps)]
five_min_maxsteps
```

# Imputing missing values
Calculate and report the total number of missing values in the dataset
Install tidyverse to replace missing values
Duplicate the dataset
```{r}
activity2 <- DataFrame
```
#Identify missing values of steps in the duplicated DataFrame
```{r}
nas <- is.na(activity2$steps)
sum(is.na(activity2))
```

replace missing value with in activyt2
```{r}
avg_interval <- tapply(activity2$steps, activity2$interval, mean, na.rm=TRUE, simplify = TRUE)
```

# Make a panel plot containing a time series plot (-= L) of the 5-minute interval 
(x-axis) and the average number of steps taken, 
averaged across all weekday days or weekend days (y-axis). 
create number of steps per date from dataset with replaced NM values
```{r}
totalstepsperday2 <- aggregate(steps ~ date, data = DataFrame, FUN = sum, na.rm = TRUE)
```

#setup frame for two graphs
```{r}
par(mfrow=c(1,2))
```
## Histogram with the orginal dataset
```{r}
hist(totalstepsperday$steps, 
     main="Total Steps per Day (Original)", 
     breaks=100)

hist(totalstepsperday2$steps, 
     main = "Total Steps per Day (no-NA)", 
     breaks=100)
```


