My First R Marckdown Doc
========================

My First markdwon file

I used I used the info [here](https://rpubs.com/sureshbk/358994) and [here](https://rstudio-pubs-static.s3.amazonaws.com/300758_367ce30144b44cd4901bedfa279bb64c.html) to complete the assignment.

# I downloaded the data set, and I set my directory 
```{r}
setwd ("C:/Users/Charlotte/Documents/GitHub/RepData_PeerAssessment1")
```

And I open/load the file
```{r}
DataFrame <- read.csv( "activity.csv")
```

spent an hr with errors trying to figure out how install packages in Kniter until I figure out on the net U don't. Why wouldn't the lectures cover that ... Wow?


# 1 Calculate the total number of steps taken per day?
Get number of steps per date and sum results removing null
```{r}
totalstepsperday <- aggregate(steps ~ date, data = DataFrame, FUN = sum, na.rm = TRUE)
```
put date in YYYYMMDD format
```{r}
DataFrame$date <- as.Date(DataFrame$date, "%Y-%m-%d")
```
Make a histogram of the total number of steps taken each day. convert dates first
A "Histograms are used to show distributions of variables while bar charts are used to compare variables.
Via [Forbes mag](https://www.forbes.com/sites/naomirobbins/2012/01/04/a-histogram-is-not-a-bar-chart/?sh=27f69e816d77)
```{r}
hist(totalstepsperday$steps, main = "steps per Day", breaks = 10)
```







